\section{Conclusion}
The medical prediction website successfully delivers a platform where users can register,
log in, submit their blood report data, and receive predictions for HCV stages
using a pretrained machine learning model. Users can view their prediction
history, while administrators have access to all prediction records
for monitoring purposes. The integration of FastAPI, Next.js, Supabase,
and Docker has resulted in a lightweight, efficient, and scalable system.

During development, several lessons were learned and challenges encountered.
Implementing the backend API with FastAPI highlighted the importance of asynchronous programming
to efficiently handle multiple requests. Integrating the machine learning model
required careful preprocessing and validation to ensure accurate predictions.
Designing the database schema and optimizing queries in Supabase was crucial for reliable 
storage and retrieval of prediction data. Deploying the application with Docker
and on cloud platforms presented challenges related to environment configuration and dependency management.
Additionally, managing overlapping frontend and backend development tasks emphasized the need for careful project scheduling.

For future improvements, the system could incorporate enhanced user authentication 
mechanisms such as OAuth or multi-factor authentication
to strengthen security. Visualization features could be added
to display prediction trends over time for each user, and
the machine learning model could be continuously retrained with anonymized
new data to improve accuracy. Notifications or email summaries could be
implemented to inform users of new predictions, and the platform could
be expanded to support additional medical conditions or lab tests.
Finally, the deployment process can be further improved with automated
CI/CD pipelines and monitoring tools to ensure reliability and maintainability.
This project lays a solid foundation for an efficient, scalable, and user-friendly
medical prediction system while providing opportunities for future enhancement.
